Concurrent Programming with CXL

### 2020-05-21 book/paper.tex
Fixes

So far we have pursued two properties: \emph{mutual exclusion}
and \emph{progress}.  The former is an example of
\texttt{safety property}---it prevents something ``bad'' from
happening, like a reader and writer process both entering the
critical section.  The \emph{progress} property is an example
of a liveness property---that something good eventually happens.
Informally (and inexactly), progress states that if no processes
are in the critical section, then some process that wants to enter
can.

Progress is a weak form of liveness.  It says that \emph{some}
process can enter, but it does not prevent a scenario such as
the following.  There are three processes repeatedly trying to
enter a critical section using a spinlock.  Two of
the processes successfully enter, alternating, but the third
process never gets a turn.  This is an example of
\texttt{starvation}.  With a spinlock, this scenario could
even happen with two processes.  Initially both processes
try to acquire the spinlock.  One of the processes is
successful and enter.  After the process leaves, it immediately
tries to re-enter.  This state is identical to the initial
state, and there is nothing that prevents the same process
from acquiring the lock yet again.

>>>>

So far we have pursued two properties: \emph{mutual exclusion}
and \emph{progress}.  The former is an example of a
\emph{safety property}---it prevents something ``bad'' from
happening, like a reader and writer process both entering the
critical section.  The \emph{progress} property is an example
of a \emph{liveness property}---guaranteeing that something good
eventually happens.
Informally (and inexactly), progress states that if no processes
are in the critical section, then some process that wants to enter
can.

Progress is a weak form of liveness.  It says that \emph{some}
process can enter, but it does not prevent a scenario such as
the following.  There are three processes repeatedly trying to
enter a critical section using a spinlock.  Two of
the processes successfully enter, alternating, but the third
process never gets a turn.  This is an example of
\texttt{starvation}.  With a spinlock, this scenario could
even happen with two processes.  Initially both processes
try to acquire the spinlock.  One of the processes is
successful and enters.  After the process leaves, it immediately
tries to re-enter.  This state is identical to the initial
state, and there is nothing that prevents the same process
from acquiring the lock yet again.
